---
title: "Writing functions"
author: "Olya Besedina"
data: "10/24/2019"
output: github_document
---
  
```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
 	echo = TRUE,
 	warning = FALSE,
 	fig.width = 8, 
   fig.height = 6,
   out.width = "90%"
 )

options(
   ggplot2.continuous.colour = "viridis",
   ggplot2.continuous.fill = "viridis"
 )

 scale_colour_discrete = scale_colour_viridis_d
 scale_fill_discrete = scale_fill_viridis_d

 theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Get started

```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = .3)
y = rnorm(n = 30, mean = 6, sd = .3)

# z scores
(x - mean (x)) / sd(x)
(x_again - mean (x_again)) / sd(x_again)


```

Now a function

```{r}
z_score = function(x) {
  
  if(!is.numeric(x)) {
    stop("x should be numeric")
  } else if(length(x) < 3){
    stop( "x should be longer than 3")
  }
  
  (x - mean(x)) / sd(x)
  
}
```

Try out the function

```{r, eval = FALSE}
z_score(x = x_again)

z_score(x = 3)
z_score (x = "my name is jeff")
z_score (x = c(TRUE, TRUE, FALSE, TRUE))
z_score(x = iris)

```

## Multiple output
If you want to create multiple output from one function you can orginize in in a tibble.

```{r}
mean_and_sd = function(input_x)
{
  
  if(!is.numeric(x)) {
    stop("x should be numeric")
  } else if(length(x) < 3){
    stop( "x should be longer than 3")
  }

  tibble(
    mean_input = mean(input_x),
    sd_input = sd(input_x)
  ) 
}

```

Test the function
```{r}
mean_and_sd(input_x = x)
```

# list - allows you to combine any number of things into one output structure
```{r}
mean_and_sd_list = function(input_x)
{
  
  if(!is.numeric(x)) {
    stop("x should be numeric")
  } else if(length(x) < 3){
    stop( "x should be longer than 3")
  }

  list(
    mean_input = mean(input_x),
    sd_input = sd(input_x),
    z_score = (input_x - mean(input_x)) / sd(input_x)
  ) 
}

```

```{r}
mean_and_sd_list(input_x = x)
```

# Multiple inputs

y is related to x through the simple linear regression

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

sim_data %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()

ls_fit = lm(y ~ x, data = sim_data)
  
# estimated intercept:
beta0_hat = coef(ls_fit)[1]
# estimated slope
beta1_hat = coef(ls_fit)[2]
```


By defauld beta0= 2, beta1 = 3 unles changed by the user

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)

# Can write in order without naming it
sim_regression(3000, beta0 = 24)
``` 


# Scrape lots of napoleon

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Now as a function

```{r}
read_page_reviews = function(page_url) {
  url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(page_url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

reviews

}

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=4")
```

# Lord of the rings data

```{r, eval = FALSE}
library(readxl)
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```

As a function

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```


```{r}
x = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x, sd)

```






